Evolution of Processes in Delivering Reliable Software within the European Scientific Arena

### 2018-09-14 paper-ieee-trans.tex
remove end parenthesis

On behalf of the quality assurance group, specific measures for the software development process and quality assurance were defined and introduced in the project. Through project monitoring and reporting mechanisms there was a successful control of the risks, efforts and document produced. The definition of a project developer's guide \cite{datagridguide} was able to provide developers with guidelines for the various software development phases (such as packaging, test and validation process, and style and naming convention) and to allow quality group to control software release via a procedure checklist.
The specification of quality indicators \cite{datagridindicators} allowed project managers to have an update view of the quality of the services over months. Figure \ref{fig:efficiency} shows the efficiency performance indicator measured as the number of jobs successfully completed divided the total number of jobs submitted: generally the project managers observed a positive trend of efficiency over months with only one exception for the LCG1 experiment due to some errors on the dedicated resources. Figure \ref{fig:bugzilla} shows the Bugzilla anomalies follow up in the second release.
\begin{figure}[ht]
\centering
\includegraphics[width=0.5\textwidth, height=50mm]{images/dgeff.png}
\caption{Efficiency \% = Number of jobs successfully completed / Total Number of jobs submitted): results are provided for five experiments involved in the projects.}
\label{fig:efficiency}
\end{figure}

>>>>

On behalf of the quality assurance group, specific measures for the software development process and quality assurance were defined and introduced in the project. Through project monitoring and reporting mechanisms there was a successful control of the risks, efforts and document produced. The definition of a project developer's guide \cite{datagridguide} was able to provide developers with guidelines for the various software development phases (such as packaging, test and validation process, and style and naming convention) and to allow quality group to control software release via a procedure checklist.
The specification of quality indicators \cite{datagridindicators} allowed project managers to have an update view of the quality of the services over months. Figure \ref{fig:efficiency} shows the efficiency performance indicator measured as the number of jobs successfully completed divided the total number of jobs submitted: generally the project managers observed a positive trend of efficiency over months with only one exception for the LCG1 experiment due to some errors on the dedicated resources. Figure \ref{fig:bugzilla} shows the Bugzilla anomalies follow up in the second release.
\begin{figure}[ht]
\centering
\includegraphics[width=0.5\textwidth, height=50mm]{images/dgeff.png}
\caption{Efficiency \% = Number of jobs successfully completed / Total Number of jobs submitted: results are provided for five experiments involved in the projects.}
\label{fig:efficiency}
\end{figure}
